Quantifying the importance of an inference model in Bayesian phylogenetics

### 2020-02-06 supplement.tex
I hope everything is OK before the Overleaf merge
Changes Giappo

\begin{figure}[H]
  \includegraphics[width=\textwidth]{pirouette_example_26/example_26_314/errors.png}
  \caption{Assuming a Yule tree prior on a BD tree}
\end{figure}

@@

>>>>

\richel{depends on https://github.com/richelbilderbeek/pirouette/issues/378}

% \begin{figure}[H]
%   \includegraphics[width=\textwidth]{pirouette_example_26/example_26_314/errors.png}
%   \caption{Assuming a Yule tree prior on a BD tree}
% \end{figure}

@@

Here we show the results of a \verb;pirouette; run on a dataset of $N = 100$ \giovanni{N can be changed if 100 is too much} trees simulated under a diversity-dependent process. All the trees are simulated using the DDD package (\cite{DDD}). Our goal is to show how trees simulated by a process that is sensibly different from a standard tree prior will result in a significant divergence between true and twin distribution. To do so we set the simulation parameters (in this case: absolute speciation rate $\lambda_0 = 1.6$, extinction rate $\mu = 0.2$ and carrying capacity $K = 20$) in order to express clear characteristics of diversity dependence in the phylogenies. In fact, for a high speciation rate and a low carrying capacity we expect trees to exhibit high unbalance, compared with trees generated by a standard birth-death model. We can measure how unbalanced is a tree using the $\gamma$ statistics (\cite{pybus2000testing}). For this reason, we choose to measure the error made by the inference process using the $\gamma$ error statistics, which is currently implemented in \verb;pirouette;.
